### 2022-05-13 Publish Paper/manuscript_main.tex
update mail teacher

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancer leading causes of death worldwide. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing
incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment. Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data. In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example. In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of the metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancer leading causes of death worldwide. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing
incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment. Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data. In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example. In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of the metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.
